Age-related changes in plant growth and traits

### 2015-04-22 results.Rmd
minor changes to each

```{r, echo=FALSE,results='hide', message=FALSE}
plot_LLvAge <- function(spp) {
  data2 <- filter(SummaryInd, species==spp)
  plot(LL_birth ~ age, data=data2, xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1,
       main=labels.spp[spp], xlim=c(1,35), ylim=c(0,8), log="x", pch=16)
  points(LL_birth_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
  points((LL_birth_mean+LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
  points((LL_birth_mean-LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)

@@

>>>>

@@

#22 April 2015
Generic code to create plots, run lm, summarize results, by species

```{r, echo=FALSE,results='hide', message=FALSE}
plot_yvar_vs_xvar <- function(data, yvar = "y", xvar = "x", ...) {
  Y <- data[[yvar]]
  X <- data[[xvar]]
  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
}

summarise_all_fits <- function(x) {
  tmp <- lapply(x, summarise_fit) %>%
    bind_rows
  data.frame(species=names(x), tmp)
}
```

#RV curves
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "ReproInv"
xvar <- "FinalWeight"

data <- filter(SummaryInd)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,plot_LLvAge <- function(spp) {
  data2 <- filter(SummaryInd, species==spp)
  plot(LL_birth ~ age, data=data2, xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1,
       main=labels.spp[spp], xlim=c(1,35), ylim=c(0,8), log="x", pch=16)
  points(LL_birth_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
  points((LL_birth_mean+LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
  points((LL_birth_mean-LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)
                    main=spp, log="xy",xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```
